Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case

### 2019-01-20 ICML-submission/notions-of-linear-separability.tex
Update notions-of-linear-separability.tex

It is easy to see that if a set of labeled examples is strongly linearly
separable with margin $\gamma$, then it is also weakly linearly separable with
the same margin. Indeed, if $w_1, w_2, \dots, w_K \in V$ satisfy
\eqref{equation:strong-linear-separability-1},
\eqref{equation:strong-linear-separability-2},
\eqref{equation:strong-linear-separability-3} then they satisfy
\eqref{equation:weak-linear-separability-1} and
\eqref{equation:weak-linear-separability-2}.

>>>>

It is easy to see that if a set of labeled examples is strongly linearly
separable with margin $\gamma$, then it is also weakly linearly separable with
the same margin (or larger). Indeed, if $w_1, w_2, \dots, w_K \in V$ satisfy
\eqref{equation:strong-linear-separability-1},
\eqref{equation:strong-linear-separability-2},
\eqref{equation:strong-linear-separability-3} then they satisfy
\eqref{equation:weak-linear-separability-1} and
\eqref{equation:weak-linear-separability-2}.
